Calculating life expectancy and exploring missingness

### 2016-10-05 Code/1_Explore_Data_v2.Rmd
added the agg decomp graphs to shiny app

#create list of stratum.ids for each race-sex combination
for (rs in unique(levels(dat.clean$RaceSex))) {
  assign(paste0(gsub(" ", "", rs), ".stratum.ids"), 
      dat.clean %>% filter(dat.clean$RaceSex == rs) %>%
        select(StateYearRaceSex, StateYearSex) %>%
        group_by(StateYearRaceSex, StateYearSex) %>%
        filter(row_number() == 1)# %>%
      #  rename(paste0(gsub(" ", "", rs), ".ids") = StateYearRaceSex)
         )

@@

#merge the black-white lists
Female.ids <- merge(WhiteFemale.stratum.ids, BlackFemale.stratum.ids, by = "StateYearSex")
Female.ids <- Female.ids %>% rename(White.StateYearRaceSex = StateYearRaceSex.x, Black.StateYearRaceSex = StateYearRaceSex.y)
Female.ids$Sex2 <- "Female"

Male.ids <- merge(WhiteMale.stratum.ids, BlackMale.stratum.ids, by = "StateYearSex")
Male.ids <- Male.ids %>% rename(White.StateYearRaceSex = StateYearRaceSex.x, Black.StateYearRaceSex = StateYearRaceSex.y)
Male.ids$Sex2 <- "Male"

@@

  if(length(white.index) != 0 & length(black.index) != 0) {
    list.age.decomp.tables[[i]] <- le_age_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]), 
                                                 name.lt1 = "Black", 
                                                 life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                                                 name.lt2 = "White", age.groups = "Age3")
  } else {
    list.age.decomp.tables[[i]] <- "Couldn't compare life tables"
  }
  print(i)
}

@@

```{r}
save(dat.clean, dat2, BlackWhite, file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

#create list of stratum.ids for each race-sex combination
for (rs in unique(levels(dat.clean$RaceSex))) {
  assign(paste0(gsub(" ", "", rs), ".stratum.ids"), 
      dat.clean %>% filter(dat.clean$RaceSex == rs) %>%
        select(StateYearRaceSex, StateYearSex, Sex2, State2, Year3) %>%
        group_by(StateYearRaceSex, StateYearSex) %>%
        filter(row_number() == 1)# %>%
      #  rename(paste0(gsub(" ", "", rs), ".ids") = StateYearRaceSex)
         )

@@

#merge the black-white lists
Female.ids <- merge(WhiteFemale.stratum.ids, BlackFemale.stratum.ids[, -c(3:5)], 
                    by = "StateYearSex", suffixes = c("White", "Black"))
head(Female.ids)

Male.ids <- merge(WhiteMale.stratum.ids, BlackMale.stratum.ids[, -c(3:5)],
                  by = "StateYearSex", suffixes = c("White", "Black"))
head(Male.ids)

@@

  if(length(white.index) != 0 & length(black.index) != 0) {
    list.age.decomp.tables[[i]] <- le_age_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]), 
                                                 name.lt1 = "Black", 
                                                 life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                                                 name.lt2 = "White", age.groups = "Age3")
  } else {
    list.age.decomp.tables[[i]] <- "Couldn't compare life tables"
  }
}
```

@@

```{r}
save(dat.clean, dat2, BlackWhite, paired.ids, list.age.decomp.tables,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```
